---
title: "Week 4 Project"
author: "Benjamin Menashe"
date: "9/26/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Spurious Correlations
Under certain circumstances, samples drawn randomly from two **independent** distributions will have a linear relationship that is significantly different than 0. This is called a "Spurious Correlation". 

## The Problem
1. If we treat a linear correlation as an indication of a relationship between the variables, such spurious correlations can make us believe independent correlations are actually dependent.
2. This gets worse if we do a correlation test and get a low p-value.
3. Lack of awareness to this problem is a problem by itself.

## Example

```{r, echo = TRUE}
set.seed(1234); n = 25; X <- rexp(n); Y <- rexp(n)
plot(X,Y); abline(lm(Y~X), col = "red")
```

## The Solution
I created a Shiny app where users can choose 2 random samples from a variety of distributions and see the spurious relationship. The samples are independent of each other. 

**I believe this will enhance awareness to the problem of spurious correlations and may serve as a useful learning tool.** 

Thanks!
